---
title: "`r countrynamet`"
author: "Commitment to Human Capital - Scorecard"
urlcolor: blue
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
    keep_tex: yes
    pandoc_args: ["-V", "classoption=twocolumn"]
fontsize: 9.2pt
geometry: "left=1.5cm,right=1.5cm,top=2.2cm,bottom=2cm"
header-includes:
  \usepackage{fancyhdr}
  \pagestyle{fancy}
  \usepackage[table]{xcolor}
  \usepackage{xcolor}
  \usepackage{graphicx}
  \usepackage{eurosym}
  \usepackage{booktabs,xcolor}
  \rhead{Africa Human Capital Project - \today}
  \rfoot[C]{\includegraphics[width=2cm]{static/footer3.png}}
  \fancypagestyle{plain}{\pagestyle{fancy}}
  \pagenumbering{gobble}
  \usepackage{pagecolor}
  \pagecolor{white}
  \usepackage{fourier}
  \usepackage[fontsize=8.7pt]{scrextend}
  \usepackage{float}
  \usepackage[utf8]{inputenc}
---

\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
\newcommand\boldblue[1]{\textcolor{bondiblue}{\textbf{#1}}}

This scorecard presents a snapshot of the country's commitment to the human capital agenda and the World Bank Group's support for the social sectors. 
 

### \boldblue{I\small{NDICATORS IN THE AFRICA HUMAN CAPITAL PLAN}}###

* **Human Capital Index.**  `r x[["hci_text"]]`

* **Adolescent Fertility Rate.** `r x[["lastafr_text"]]`

* **Social Protection Coverage.** `r x[["lastspc_text"]]`

* **Open Defecation.** `r x[["lastod_text"]]`

### \boldblue{I\small{NDICATORS ON WOMEN'S EMPOWERMENT}}###

* **Total Fertility Rate.** `r x[["lasttfr_text"]]`

* **Contraceptive Prevalence.** `r x[["contracep_text"]]`

* **Women, Business and the Law Index.** `r x[["wbl_text"]]` 

* **Net Enrolment Rate in Secondary School.** `r x[["lastner_sec_f_text"]]`


### \boldblue{D\small{OMESTIC RESOURCE USE AND MOBILIZATION}}###

* **Health Spending.** `r x[["health_text"]]`

* **Education Spending.** `r x[["edu_text"]]`

* **Social Protection Spending.** `r x[["socprot_text"]]`

```{r out.width = "100%", fig.align = "right", echo=FALSE}
gr1 <- paste0("charts/all_mf_", x[["wbcode"]], ".pdf")
knitr::include_graphics(gr1)
```

```{r out.width = "100%", out.height="120%", fig.align = "right", echo=FALSE, strip.white=TRUE}
gr2 <- paste0("charts/socsec_", x[["wbcode"]], ".pdf")
knitr::include_graphics(gr2)
```
\vspace{3mm}

* **Efficiency of Spending.** `r x[["eff_text"]]`

```{r out.width = "100%", out.height="50%", fig.align = "center", echo=FALSE, strip.white=TRUE}
gr3 <- paste0("charts/efficiency_", x[["wbcode"]], ".pdf")
knitr::include_graphics(gr3)
```

* **Domestic Resource Mobilization.** `r x[["drm_text"]]`

```{r out.width = "100%", out.height="50%", fig.align = "right", echo=FALSE}
gr4 <- paste0("charts/drm_", x[["wbcode"]], ".pdf")
knitr::include_graphics(gr4)
```

### \boldblue{O\small{THER RELEVANT INDICATORS }}#####

* **Human Capital Project.** `r x[["hci_memt"]]`

* **Building Human Capital.** `r x[["cpia_text"]]`

* **Identification.** `r x[["ident_text"]]`

* **Statistical Data on Human Capital.** `r x[["stat_text"]]`

### \boldblue{H\small{OW IS THE WORLD BANK SUPPORTING THE EFFORT?}}#####

The following table summarizes the World Bank's investments in Human Development for `r countrynameb`, including measures of volume, performance, and other relevant indicators.

\definecolor{asparagus}{RGB}{3, 158, 115}
\definecolor{blush}{RGB}{204 121 167}
\definecolor{arylideyellow}{RGB}{230 159 0}
\definecolor{blue(ncs)}{rgb}{0.0, 0.53, 0.74}
\definecolor{ashgrey}{rgb}{0.7, 0.75, 0.71}
\definecolor{bleudefrance}{rgb}{0.19, 0.55, 0.91}
\definecolor{iceberg}{rgb}{0.44, 0.65, 0.82}
\begin{table}[H]
\small
\begin{tabular}{lcccc}
`r rl[[1]]` \\ \hline
`r rl[[2]]` \\ \hline
`r rl[[3]]` \\ \hline
`r rl[[4]]` & `r x[["hdportfolio"]]` & `r x[["eduportfolio"]]` & `r x[["hnpportfolio"]]` & `r x[["spjportfolio"]]` \\ 
`r rl[[5]]` & `r x[["hdportfolio_share"]]` & `r x[["eduportfolio_share"]]` & `r x[["hnpportfolio_share"]]` & `r x[["spjportfolio_share"]]` \\ 
`r rl[[6]]` & `r x[["hdportfolio_share_diffmr"]]` & `r x[["eduportfolio_share_diffmr"]]` & `r x[["hnpportfolio_share_diffmr"]]` & `r x[["spjportfolio_share_diffmr"]]` \\ 
`r rl[[7]]` & `r x[["hdportfolio_share_diffmi"]]` & `r x[["eduportfolio_share_diffmi"]]` & `r x[["hnpportfolio_share_diffmi"]]` & `r x[["spjportfolio_share_diffmi"]]` \\ \hline
`r rl[[8]]` \\ \hline 
`r rl[[9]]` & `r x[["pipeline_hd"]]` & `r x[["pipeline_edu"]]` & `r x[["pipeline_hnp"]]` & `r x[["pipeline_spj"]]` \\ 
`r rl[[10]]` & `r x[["pipeline_hd_share"]]` & `r x[["pipeline_edu_share"]]` & `r x[["pipeline_hnp_share"]]` & `r x[["pipeline_spj_share"]]` \\ 
`r rl[[11]]` & `r x[["pipeline_hd_share_diffmr"]]` & `r x[["pipeline_edu_share_diffmr"]]` & `r x[["pipeline_hnp_share_diffmr"]]` & `r x[["pipeline_spj_share_diffmr"]]` \\ 
`r rl[[12]]` & `r x[["pipeline_hd_share_diffmi"]]` & `r x[["pipeline_edu_share_diffmi"]]` & `r x[["pipeline_hnp_share_diffmi"]]` & `r x[["pipeline_spj_share_diffmi"]]` \\ \hline
`r rl[[13]]` \\ \hline
`r rl[[14]]` & `r x[["do_performance_hd"]]` & `r x[["do_performance_edu"]]` & `r x[["do_performance_hnp"]]` & `r x[["do_performance_spj"]]` \\ 
`r rl[[15]]` & `r x[["do_performance_hd_diffmr"]]` & `r x[["do_performance_edu_diffmr"]]` & `r x[["do_performance_hnp_diffmr"]]` & `r x[["do_performance_spj_diffmr"]]` \\ 
`r rl[[16]]` & `r x[["do_performance_hd_diffmi"]]` & `r x[["do_performance_edu_diffmi"]]` & `r x[["do_performance_hnp_diffmi"]]` & `r x[["do_performance_spj_diffmi"]]` \\ 
`r rl[[17]]` & `r x[["percsatisfdo_hd"]]` & `r x[["percsatisfdo_edu"]]` & `r x[["percsatisfdo_hnp"]]` & `r x[["percsatisfdo_spj"]]` \\ 
`r rl[[18]]` & `r x[["ip_performance_hd"]]` & `r x[["ip_performance_edu"]]` & `r x[["ip_performance_hnp"]]` & `r x[["ip_performance_spj"]]` \\ 
`r rl[[19]]` & `r x[["ip_performance_hd_diffmr"]]` & `r x[["ip_performance_edu_diffmr"]]` & `r x[["ip_performance_hnp_diffmr"]]` & `r x[["ip_performance_spj_diffmr"]]` \\ 
`r rl[[20]]` & `r x[["ip_performance_hd_diffmi"]]` & `r x[["ip_performance_edu_diffmi"]]` & `r x[["ip_performance_hnp_diffmi"]]` & `r x[["ip_performance_spj_diffmi"]]` \\ 
`r rl[[21]]` & `r x[["percsatisfip_hd"]]` & `r x[["percsatisfip_edu"]]` & `r x[["percsatisfip_hnp"]]` & `r x[["percsatisfip_spj"]]` \\ 
`r rl[[22]]` & `r x[["disburratio_hd"]]` & `r x[["disburratio_edu"]]` & `r x[["disburratio_hnp"]]` & `r x[["disburratio_spj"]]` \\ 
`r rl[[23]]` & `r x[["disburratio_hd_diffmr"]]` & `r x[["disburratio_edu_diffmr"]]` & `r x[["disburratio_hnp_diffmr"]]` & `r x[["disburratio_spj_diffmr"]]` \\ 
`r rl[[24]]` & `r x[["disburratio_hd_diffmi"]]` & `r x[["disburratio_edu_diffmi"]]` & `r x[["disburratio_hnp_diffmi"]]` & `r x[["disburratio_spj_diffmi"]]` \\ \hline
`r rl[[25]]` \\ \hline
`r rl[[26]]` & `r x[["avgsize_hd"]]` & `r x[["avgsize_edu"]]` & `r x[["avgsize_hnp"]]` & `r x[["avgsize_spj"]]` \\ 
`r rl[[27]]` & `r x[["avgsize_hd_diffmr"]]` & `r x[["avgsize_edu_diffmr"]]` & `r x[["avgsize_hnp_diffmr"]]` & `r x[["avgsize_spj_diffmr"]]` \\ 
`r rl[[28]]` & `r x[["avgsize_hd_diffmi"]]` & `r x[["avgsize_edu_diffmi"]]` & `r x[["avgsize_hnp_diffmi"]]` & `r x[["avgsize_spj_diffmi"]]` \\ 
`r rl[[29]]` & `r x[["crossgpshare_hd"]]` & `r x[["crossgpshare_edu"]]` & `r x[["crossgpshare_hnp"]]` & `r x[["crossgpshare_spj"]]` \\ 
`r rl[[30]]` & `r x[["crossgpshare_hd_diffmr"]]` & `r x[["crossgpshare_edu_diffmr"]]` & `r x[["crossgpshare_hnp_diffmr"]]` & `r x[["crossgpshare_spj_diffmr"]]` \\ 
`r rl[[31]]` & `r x[["crossgpshare_hd_diffmi"]]` & `r x[["crossgpshare_edu_diffmi"]]` & `r x[["crossgpshare_hnp_diffmi"]]` & `r x[["crossgpshare_spj_diffmi"]]` \\ \hline
 \multicolumn{5}{l}{Note: a) \colorbox{blush}{Pink} indicates that the value is within the first tercile of the} \\
 \multicolumn{5}{l}{distribution for all the countries. \colorbox{arylideyellow}{Orange} indicates that the value is } \\
 \multicolumn{5}{l}{within the second tercile. \colorbox{asparagus}{Green} indicates that it is within the third} \\
 \multicolumn{5}{l}{tercile. b) FY20 lending program includes only projects rated A and B. c) DO and IP are } \\
 \multicolumn{5}{l}{on a scale of 1 to 6 where 1 is Highly Unsatisfactory and 6 is Highly Satisfactory. d( Data) } \\
 \multicolumn{5}{l}{as of September 5, 2019.} \\
\end{tabular}
\end{table}

* **Human Capital Policy Operations.** `r x[["dpohc_text"]]`

* **Women's Empowerment Project.** `r x[["wep_text"]]`

\noindent\rule{9cm}{0.4pt}
This scorecard is intended to be a conversation starter on where a country is on various aspects of human capital development and the state of the World Bank's support in the social sectors. The list of indicators presented here is not exhaustive and should be complemented with more context specific variables. Most of the indicators are related to the Africa Human Capital Plan.
&nbsp;

The sources of data for the different indicators include: the Human Capital Project, the World Development Indicators, and the World Bank's internal system to monitor investments.
&nbsp;

For more information, please contact the Africa Human Capital Project team: AFR_HCP_Team@worldbankgroup.org 
