---
title: "`r countrynamet`"
author: "Illustrative Human Capital Indicators"
urlcolor: blue
output:
  pdf_document:
   latex_engine: xelatex
   fig_caption: yes
   keep_tex: yes
fontsize: 9.2pt
geometry: "left=1.3cm,right=1.3cm,top=2cm,bottom=2cm"
header-includes:  \usepackage{fancyhdr}
  \usepackage{graphicx}
  \usepackage{eurosym}
  \usepackage{booktabs,xcolor} \pagestyle{fancy}
  \rhead{Human Capital Project - \today}
  \rfoot{}  
  \lfoot{\includegraphics[width=19.5cm]{static/footerpdf.pdf}} 
  \fancypagestyle{plain}{\pagestyle{fancy}}
  \pagenumbering{gobble}
  \usepackage{pagecolor}
  \pagecolor{white}
  \usepackage{fourier}
  \usepackage[fontsize=8.7pt]{scrextend}
  \usepackage{float}
  \restylefloat{table}
  \usepackage{xcolor}
  \usepackage{multicol}
  \newcommand{\hideFromPandoc}[1]{#1}
  \hideFromPandoc{
    \let\Begin\begin
    \let\End\end
  }
  \usepackage{caption}
  \captionsetup{skip=0pt} 
---

\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
\newcommand\boldblue[1]{\textcolor{bondiblue}{\textbf{#1}}}
  
This country profile presents a snapshot of illustrative indicators to guide discussions during the Annual Meetings while the set of more strategic indicators are under development. It is intended to be a conversation starter on where a country is on various aspects of human capital development and, as such, it includes indicators from various sectors. It is to be noted that not all the indicators included here are relevant for each country. Information contained here should be complemented with other more context-specific indicators. 

`r x[["hci_text"]]`

\Begin{multicols}{2}

### \boldblue{I\small{LLUSTRATIVE OUTCOME AND OUTPUT INDICATORS}}###

* **Women, Business and the Law Index.** `r x[["wbl_text"]]` 

* **Adolescent Fertility Rate.** `r x[["lastafr_text"]]`

* **Contraceptive Prevalence.** `r x[["contracep_text"]]`

* **Social Protection Coverage.** `r x[["lastspc_text"]]`

* **Open Defecation.** `r x[["lastod_text"]]`

* **Hygiene.** `r x[["hygiene_basic_text"]]`

* **Source of Drinking Water.** `r x[["water_text"]]`

* **Cooking Fuel.** `r x[["clean_fuel_text"]]`

* **Access to Electricity.** `r x[["electric_text"]]`

* **Road Traffic Deaths.** `r x[["road_traff_text"]]`

```{r out.width = "100%", fig.align = "right", echo=FALSE}
gr1 <- paste0("charts/all_mf_", x[["wbcode"]], ".pdf")
knitr::include_graphics(gr1)
```

### \boldblue{D\small{OMESTIC RESOURCE USE AND MOBILIZATION}}###

* **Health Spending.** `r x[["health_text"]]`

* **Education Spending.** `r x[["edu_text"]]`

* **Social Assistance Spending.** `r x[["socprot_text"]]`

```{r out.width = "100%", out.height="120%", fig.align = "right", echo=FALSE, strip.white=TRUE}
gr2 <- paste0("charts/socsec_", x[["wbcode"]], ".pdf")
knitr::include_graphics(gr2)
```
\vspace{3mm}

* **Efficiency of Spending.** `r x[["eff_text"]]`

```{r out.width = "100%", out.height="50%", fig.align = "center", echo=FALSE, strip.white=TRUE}
gr3 <- paste0("charts/efficiency_", x[["wbcode"]], ".pdf")
knitr::include_graphics(gr3)
```

* **Domestic Resource Mobilization.** `r x[["drm_text"]]`

```{r out.width = "100%", out.height="50%", fig.align = "right", echo=FALSE}
gr4 <- paste0("charts/drm_", x[["wbcode"]], ".pdf")
knitr::include_graphics(gr4)
```

### \boldblue{O\small{THER RELEVANT INDICATORS }}#####

* **Human Capital Project.** `r x[["hci_memt"]]`

* **Building Human Capital.** `r x[["cpia_text"]]`

* **Identification.** `r x[["ident_text"]]`


\noindent\rule{9cm}{0.4pt}
 &nbsp;
  
This country profile is based on most recent data available under the Human Capital Project, the World Development Indicators, Atlas of Social Protection - Indicators of Resilience and Equity (ASPIRE) and Identification for Development (ID4D).
  &nbsp;
  
For more information on data sources, please contact the Human Capital Project team: humancapital@worldbank.org.  

\End{multicols}
