---
title: "Ethiopia"
author: "Commitment to Human Capital - Scorecard"
urlcolor: blue
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
    keep_tex: yes
    pandoc_args: ["-V", "classoption=twocolumn"]
fontsize: 9.2pt
geometry: "left=1.5cm,right=1.5cm,top=2.2cm,bottom=2.2cm"
header-includes:
  \usepackage{fancyhdr}
  \pagestyle{fancy}
  \usepackage[table]{xcolor}
  \usepackage{xcolor}
  \usepackage{graphicx}
  \usepackage{eurosym}
  \usepackage{booktabs,xcolor}
  \rhead{Africa Human Capital Project - \today}
  \rfoot[C]{\includegraphics[width=2cm]{static/footer3.png}}
  \fancypagestyle{plain}{\pagestyle{fancy}}
  \pagenumbering{gobble}
  \usepackage{pagecolor}
  \pagecolor{white}
  \usepackage{fourier}
  \usepackage[fontsize=8.7pt]{scrextend}
  \usepackage{float}
  \usepackage[utf8]{inputenc}
---

\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
\newcommand\boldblue[1]{\textcolor{bondiblue}{\textbf{#1}}}

This note presents a snapshot of the country's commitment on the human capital agenda and the main actions being taken by the World Bank Group to support the government. 

### \boldblue{H\small{UMAN CAPITAL CONTEXT}}###

*  `r x[["hci_text"]]` 

* **Social Protection Coverage**  `r x[["lastspc_text"]]`

* **Open Defecation.**  `r x[["lastod_text"]]`


### \boldblue{W\small{OMEN'S EMPOWERMENT}}###
* **Total Fertility Rate.**  `r x[["lasttfr_text"]]`

* **Adolescent Fertility Rate.**  `r x[["lastafr_text"]]`

* **Contraceptive Prevalence.**  `r x[["contracep_text"]]`

* **Women, Business and the Law Index.**  `r x[["wbl_text"]]` 

* **Net Enrolment Rate in Secondary School.**  `r x[["lastner_sec_f_text"]]`

### \boldblue{W\small{HOW IS THE COUNTRY DOING?}}###
`r x[["hci_memt"]]`

* **Health Spending.** `r x[["health_text"]]`

* **Education Spending.** `r x[["edu_text"]]`

* **Social Protection Spending.** `r x[["socprot_text"]]`

```{r out.width = "100%", fig.align = "right", echo=FALSE}
knitr::include_graphics("charts/all_mf_ETH.pdf")
```
\vspace{3mm}
```{r out.width = "100%", out.height="120%", fig.align = "right", echo=FALSE, strip.white=TRUE}
knitr::include_graphics("charts/socsec_ETH.pdf")
```
\vspace{3mm}

* **Efficiency of Spending.** `r x[["eff_text"]]`

```{r out.width = "100%", out.height="50%",  fig.align = "center", echo=FALSE, strip.white=TRUE}
knitr::include_graphics("charts/efficiency_ETH.pdf")
```

* **Domestic Resource Mobilization.** `r x[["drm_text"]]`

```{r out.width = "100%", out.height="50%", fig.align = "right", echo=FALSE}
knitr::include_graphics("charts/drm_ETH.pdf")
```

* **Building Human Capital.** `r x[["cpia_text"]]`

* **Identification** `r x[["ident_text"]]`

* **Statistical Data on Human Capital** `r x[["stat_text"]]`

### \boldblue{H\small{OW IS THE WORLD BANK SUPPORTING THE EFFORT?}}#####

The following table summarizes the World Bank investments in Human Development for Ethiopia, including measures of volume, performance, and other relevant indicators.

\definecolor{asparagus}{RGB}{3, 158, 115}
\definecolor{blush}{RGB}{204 121 167}
\definecolor{arylideyellow}{RGB}{230 159 0}
\definecolor{blue(ncs)}{rgb}{0.0, 0.53, 0.74}
\definecolor{ashgrey}{rgb}{0.7, 0.75, 0.71}
\definecolor{bleudefrance}{rgb}{0.19, 0.55, 0.91}
\definecolor{iceberg}{rgb}{0.44, 0.65, 0.82}
\begin{table}[H]
\small
\begin{tabular}{lcccc}
`r rl[[1]]` \\\hline
`r rl[[2]]` & \cellcolor{iceberg} & \cellcolor{iceberg} & \cellcolor{iceberg} & \cellcolor{iceberg} \\ 
\hline
 \multicolumn{5}{l}{Note: a) Pink indicates that the value is within the first tercile of the} \\
 \multicolumn{5}{l}{distribution for all the countries. Orange indicates that the value is } \\
 \multicolumn{5}{l}{is within the second tercile. Green indicates that it is within the third} \\
 \multicolumn{5}{l}{tercile. b) FY20 lending program includes only projects rated A, B and } \\
 \multicolumn{5}{l}{unrated. c) DO and IP are on a scale of 1 to 5 where 1 is Unsatisfactory } \\
 \multicolumn{5}{l}{and5 is Highly Satisfactory. d) Data as of July 15, 2019.} \\
\end{tabular}
\end{table}

* **Human Capital Policy Operations.** Currently, the pipeline for Ethiopia **does not** include any Development Policy Operations with a Human Capital-related component or prior action.

* **Women Empowerment Project.** Currently, Ethiopia **does not** have an active project focused on women empowerment or on sexual and reproductive health.

\noindent\rule{9cm}{0.4pt}
The present scorecard aims to be a conversation starter on some of the main indicators that show progress towards human capital outcomes. The list of indicators presented here is not exhaustive and should be complemented with more specific variables.
&nbsp;

The sources for the different indicators come from the Human Capital Project, the World Development Indicators, and the World Bank's internal system to monitor investments.
&nbsp;

For more information, please contact the Africa Human Capital team: AFR_HCP_Team@worldbankgroup.org 


