---
title: "`r countrynamet`"
author: "Key Human Capital Indicators"
urlcolor: blue
output:
  pdf_document:
   latex_engine: xelatex
   fig_caption: yes
   keep_tex: yes
fontsize: 9.2pt
geometry: "left=1.5cm,right=1.5cm,top=2.2cm,bottom=2.2cm"
header-includes:  \usepackage{fancyhdr}
  \usepackage{graphicx}
  \usepackage{eurosym}
  \usepackage{booktabs,xcolor} \pagestyle{fancy}
  \rhead{Human Capital Project - \today}
  \rfoot{}  
  \lfoot{\includegraphics[width=19.5cm]{static/footerpdf.pdf}} 
  \fancypagestyle{plain}{\pagestyle{fancy}}
  \pagenumbering{gobble}
  \usepackage{pagecolor}
  \pagecolor{white}
  \usepackage{fourier}
  \usepackage[fontsize=8.7pt]{scrextend}
  \usepackage{float}
  \restylefloat{table}
  \usepackage{xcolor}
  \usepackage{multicol}
  \newcommand{\hideFromPandoc}[1]{#1}
  \hideFromPandoc{
    \let\Begin\begin
    \let\End\end
  }
  \usepackage{caption}
  \captionsetup{skip=0pt} 
---

\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
\newcommand\boldblue[1]{\textcolor{bondiblue}{\textbf{#1}}}
  
This country profile presents a snapshot of key indicators that countries need to monitor in the context of human capital development. It is intended to be a conversation starter on where a country is on various aspects of human capital development. The choice of indicators is, to a large extent, driven by what is most relevant for the two regions with the lowest HCI scores (Sub-Saharan Africa and South Asia). As such, not all the indicators included here are relevant for each country. Information contained here should be complemented with other more context specific indicators. 

 `r x[["hci_text"]]`

\Begin{multicols}{2}

### \boldblue{K\small{EY OUTCOME AND OUTPUT INDICATORS TO MONITOR}}###

* **Women, Business and the Law Index.** `r x[["wbl_text"]]` 

* **Adolescent Fertility Rate.** `r x[["lastafr_text"]]`

* **Contraceptive Prevalence.** `r x[["contracep_text"]]`

* **Social Protection Coverage.** `r x[["lastspc_text"]]`

* **Open Defecation.** `r x[["lastod_text"]]`

* **Hygiene.** `r x[["hygiene_basic_text"]]`

* **Source of Drinking Water.** `r x[["water_text"]]`

* **Cooking Fuel.** `r x[["clean_fuel_text"]]`

* **Access to Electricity.** `r x[["electric_text"]]`

* **Road Traffic Deaths.** `r x[["road_traff_text"]]`

```{r out.width = "100%", fig.align = "right", echo=FALSE}
gr1 <- paste0("charts/all_mf_", x[["wbcode"]], ".pdf")
knitr::include_graphics(gr1)
```

### \boldblue{D\small{OMESTIC RESOURCE USE AND MOBILIZATION}}###

* **Health Spending.** `r x[["health_text"]]`

* **Education Spending.** `r x[["edu_text"]]`

* **Social Protection Spending.** `r x[["socprot_text"]]`

```{r out.width = "100%", out.height="120%", fig.align = "right", echo=FALSE, strip.white=TRUE}
gr2 <- paste0("charts/socsec_", x[["wbcode"]], ".pdf")
knitr::include_graphics(gr2)
```
\vspace{3mm}

* **Efficiency of Spending.** `r x[["eff_text"]]`

```{r out.width = "100%", out.height="50%", fig.align = "center", echo=FALSE, strip.white=TRUE}
gr3 <- paste0("charts/efficiency_", x[["wbcode"]], ".pdf")
knitr::include_graphics(gr3)
```

* **Domestic Resource Mobilization.** `r x[["drm_text"]]`

```{r out.width = "100%", out.height="50%", fig.align = "right", echo=FALSE}
gr4 <- paste0("charts/drm_", x[["wbcode"]], ".pdf")
knitr::include_graphics(gr4)
```

### \boldblue{O\small{THER RELEVANT INDICATORS }}#####

* **Human Capital Project.** `r x[["hci_memt"]]`

* **Building Human Capital.** `r x[["cpia_text"]]`

* **Identification.** `r x[["ident_text"]]`


\noindent\rule{9cm}{0.4pt}
 &nbsp;
  
Indicators in this country profile come from the Human Capital Project and the World Development Indicators.
  &nbsp;
  
For more information, please contact the Human Capital Project team: HCP_Team@worldbank.org 

\End{multicols}
